---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/dirkschumacher/ROI.plugin.cbc.svg?branch=master)](https://travis-ci.org/dirkschumacher/ROI.plugin.cbc)
[![Coverage Status](https://codecov.io/gh/dirkschumacher/ROI.plugin.cbc/branch/master/graph/badge.svg)](https://codecov.io/gh/dirkschumacher/ROI.plugin.cbc)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ROI.plugin.cbc)](https://cran.r-project.org/package=ROI.plugin.cbc)

# ROI plugin for COIN-OR branch and cut (CBC) solver

The package makes [rcbc](https://github.com/dirkschumacher/rcbc) available as a `ROI` plugin.
This is work in progress, but already usable. 

## Install

First install [rcbc](https://github.com/dirkschumacher/rcbc), then:

```{r, eval=FALSE}
devtools::install_github("dirkschumacher/ROI.plugin.cbc")
```


## Contribution

Feel free to open issues and send PRs.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.